On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-08-01 paper/paper.tex
wibble

There is other recent work using deep embeddings in functional languages for 
system development.  One example is the Ivory language \cite{Elliott2015-Ivory} 
which provides a deeply embedded DSL for use in programming high assurance
systems,  However, it's syntax is typical of a deep EDSL and requires additional
keywords and structures above idiomatic Haskell.

>>>>

There is other recent work using deep embeddings in functional languages for 
system development.  One example is the Ivory language \cite{Elliott2015-Ivory} 
which provides a deeply embedded DSL for use in programming high assurance
systems,  However, its syntax is typical of a deep EDSL and requires additional
keywords and structures above idiomatic Haskell.
